User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R memory models of tag retrieval

### 2013-11-05 writeups/proposal/proposal.tex
foo
Former-commit-id: 27fd11485aa5822e8f449e3ae41f43914ca3ea11 [formerly e4890c68f65f48386999ec46b9d5b5a228cd04a1]
Former-commit-id: 588000624b447413b7624b0f66fd1dd6da270a9f
foo
Former-commit-id: 121441ae8e2b8f8a9d07e29eadbd4f7fbeba92fe [formerly bac466661c1542099fcc2ea310ac08748c62b11b]
Former-commit-id: 126f285cb73d70b1a67ed1f820e08a7605979564

@@

ACT-R's declarative memory and vector-based memory systems are substantially different in their mathematical structure.
Nonetheless, both can successfully model classic behavioral patterns found in word pairing experiments (e.g., the ``fan effect'' \parencite{Rutledge2008}).
I will extend the work done by \textcite{Rutledge2008} by formally comparing these two models on large-scale hashtag prediction tasks.
I'll also replace the vector-based model used by \textcite{Rutledge2008} with an improved and simplified random-permutation model \parencite{Sahlgren2008}.
The primary objective is to compare the random-permutation vector-based model to ACT-R's declarative memory theory.

>>>>

% http://tex.stackexchange.com/questions/36423/random-unwanted-space-between-paragraphs
\raggedbottom

@@

ACT-R's declarative memory and vector-based memory systems are substantially different in their mathematical structure.
Nonetheless, both can successfully model classic behavioral patterns found in word pairing experiments (e.g., \cite{Rutledge2008} modeling the ``fan effect'').
I will extend the work done by \citeauthor{Rutledge2008} by formally comparing these two models on large-scale hashtag prediction tasks.
I'll also replace the vector-based model used by \citeauthor{Rutledge2008} with an improved and simplified random-permutation model \parencite{Sahlgren2008}.
The primary objective is to compare the random-permutation vector-based model to ACT-R's declarative memory theory.
